---
title: "Penguin Body Mass by Species: R"
author: "Chengyan Zhao"
date: "2026-09-24"
---
# Topic:
How does body mass vary among the three penguin species in the Palmer Penguins dataset? I will check missing values, calculate a summary for each species, and plot the measurements.

Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/),
collected by Dr. Kristen Gorman and the Palmer Station Antarctica LTER Program.
Licence: [CC0](https://creativecommons.org/publicdomain/zero/1.0/).

```{r}
#| message: false
#| warning: false
library(palmerpenguins)
library(dplyr)
library(ggplot2)

penguins |> count(species)
```

The dataset contains three species. And beofre comparing body mass, I will check how many measurements are missing.

```{r}
penguins |>
  summarise(
    total_rows = n(),
    missing_body_mass = sum(is.na(body_mass_g))
  )

mass_summary <- penguins |>
  filter(!is.na(body_mass_g)) |>
  group_by(species) |>
  summarise(
    penguins = n(),
    mean_mass_g = round(mean(body_mass_g), 1),
    .groups = "drop"
  )

mass_summary
```

The table compares the number of recorded body masses and their mean for each species. I excluded missing body mass values from the calculation.

```{r}
#| label: fig-penguin-mass-r
#| fig-cap: "Body mass measurements by penguin species."
ggplot(
  penguins |> filter(!is.na(body_mass_g)),
  aes(x = species, y = body_mass_g, fill = species)
) +
  geom_boxplot() +
  labs(x = "Species", y = "Body mass (g)") +
  theme_minimal() +
  guides(fill = "none")
```

The plot shows both the differences between species and the variation within each species. The summary table identifies which species has the highest mean; the boxplots show that individual penguins also vary in mass.